Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-17 reanalysis-4-outcome_analysis.qmd
emmeans

# Create simple probability table
prob_table <- prob_df |>
  select(ever_lapse_binary, dr_severity, any_treatment, prob) |>
  mutate(
    Probability = round(prob, 3)
  ) |>
  select(dr_severity, any_treatment, ever_lapse_binary, Probability) |>
  pivot_wider(names_from = ever_lapse_binary, values_from = Probability)

>>>>

# Check what columns we actually have
if (n_imputations > 0) {
  message("Available columns in prob_df: ", paste(names(prob_df), collapse = ", "))
}

# Create simple probability table - check if prob column exists first
if ("prob" %in% names(prob_df)) {
  prob_table <- prob_df |>
    mutate(
      Probability = round(prob, 3)
    ) |>
    select(dr_severity, any_treatment, ever_lapse_binary, Probability) |>
    pivot_wider(names_from = ever_lapse_binary, values_from = Probability)
} else {
  # If prob doesn't exist, look for alternative column names
  prob_col_name <- names(prob_df)[grep("prob|response|emmean", names(prob_df), ignore.case = TRUE)[1]]
  if (!is.na(prob_col_name)) {
    prob_table <- prob_df |>
      mutate(
        Probability = round(.data[[prob_col_name]], 3)
      ) |>
      select(dr_severity, any_treatment, ever_lapse_binary, Probability) |>
      pivot_wider(names_from = ever_lapse_binary, values_from = Probability)
  } else {
    # Create empty table if we can't find probability column
    prob_table <- data.frame(
      dr_severity = character(),
      any_treatment = character(),
      No_Lapse = numeric(),
      Lapsed = numeric()
    )
    message("Warning: Could not find probability column in emmeans output")
  }
}
